Location of Salmon Farms

### 2021-02-12 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
finished updating data quality flags. Still need to buffer points into water for some

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c)

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY)

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA")

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry)

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN")

@@

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT")

@@

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN")

@@

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN")

@@

farms_sau <- data.frame(lat = c(20.287253),
                        lon = c(40.030864)) %>%
  mutate(iso3c = "SAU")

@@

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS")

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE")

@@

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN")

@@

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN")

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI")

@@

```{r}
farms_egy <- data.frame(lat = c(31.360400495764903, 31.15023941171644, 31.319036258284083, 31.491306679824632, 31.52619128473819, 31.275726202441984, 29.944394112057978, 27.80632012228518),
                        lon = c(27.236078999801336, 29.81109569981684, 30.225935332660324, 31.4278324391214, 31.849352783373792, 32.30190584291966, 32.54627145839493,  34.29387671355847),
                        rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
  mutate(iso3c = "EGY")

@@

```{r}
farms_ind <- data.frame(lat = c(9.28696221512509),
                        lon = c(79.13007737814245)) %>%
  mutate(iso3c = "IND")

@@

farms_sgp_final <- farms_sgp %>%
  mutate(iso3c = "SGP")

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(2.131733588116292, 2.8071936098459522, 5.384539285193906, 2.8056383383493353, 2.1305137929032876),
                        lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
  mutate(iso3c = "MYS")

@@

```{r}
farms_bgd <- data.frame(lat=c(21.802433819366538),
                        lon=c(90.40418040967)) %>%
  mutate(iso3c = "BGD")

@@

```{r}
farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
  mutate(iso3c = "KHM")

@@

farms_kor_final <- farms_kor %>%
  mutate(iso3c = "KOR")

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL")

@@

```{r}
farms_hkg <- data.frame(lat_lon = c("22.537974350807968, 114.22465750899093", "22.549021238266082, 114.27266261841545", "22.549243173819686, 114.29054140885648", "22.545901930448537, 114.29912254835972", "22.524524976629923, 114.28385013462695", "22.507936457313377, 114.30641749235996", "22.47796934657302, 114.35412559932351", "22.459641511472412, 114.360272945696", "22.4435502213444, 114.35400029960742", "22.46853714662761, 114.2720207303674", "22.42337637093222, 114.27819733339493", "22.349528341786087, 114.35178911904846", "22.367924650829952, 114.31997002657292", "22.368469602475702, 114.3230438982345", "22.3691151827537, 114.30143307907038", "22.341819373881275, 114.31744391160476", "22.35464650188533, 114.26990023341041", "22.274992746117093, 114.29389242171153", "22.164051938726015, 114.25252757025574", "22.20591578796148, 114.12923505969019", "22.221779736133797, 114.12958553008323", "22.352165476146805, 114.05569941361628", "22.45358281100093, 114.2079128367368", "22.235400816169882, 114.00599898096631", "22.454708931476908, 114.22148845386273", "22.25579039550771, 114.28554310187128")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
  mutate(iso3c = "HKG")

@@

write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)

>>>>

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_eu_final <- cbind(farms_eu, eu_countries) %>%
  dplyr::select(-geometry) %>%
  mutate(iso3c = case_when(
    COUNTRY == "Spain" ~ "ESP",
    COUNTRY == "Cyprus" ~ "CYP", 
    COUNTRY == "Norway" ~ "NOR", 
    COUNTRY == "Greece" ~ "GRC",
    COUNTRY == "Malta" ~ "MLT"
  )) %>%
  dplyr::select(-COUNTRY) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ita <- data.frame(do.call(rbind, st_geometry(ita_pts_latlon))) 
names(farms_ita) <- c("lon", "lat")
farms_ita <- farms_ita %>%
  mutate(iso3c="ITA") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_fra <- data.frame(do.call(rbind, st_geometry(fra_pts_latlon))) 
names(farms_fra) <- c("lon", "lat")
farms_fra <- farms_fra %>%
  cbind(countries) %>%
  mutate(iso3c = ifelse(country == "France", "FRA", "ISR")) %>%
  dplyr::select(-country, -geometry) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_idn <- data.frame(do.call(rbind, st_geometry(idn_pts_latlon))) 
names(farms_idn) <- c("lon", "lat")
farms_idn <- farms_idn %>%
  mutate(iso3c = "IDN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_prt_final <- farms_prt %>%
  mutate(iso3c = "PRT") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_irn <- data.frame(lat = c(37.392419247868425),
                        lon = c(50.1602963496454)) %>%
  mutate(iso3c = "IRN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_chn <- data.frame(lat = c(26.649767732301385),
                        lon = c(119.94149300994019)) %>%
  mutate(iso3c = "CHN") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_sau <- data.frame(lat = c(20.27293672234808),
                        lon = c(40.03614937279944)) %>%
  mutate(iso3c = "SAU") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_mus <- data.frame(lat = c(-20.005039247819017),
                        lon = c(57.67022708374523)) %>%
  mutate(iso3c = "MUS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

farms_are <- data.frame(lat = c(25.604715925918068),
                        lon = c(56.340214330776234)) %>%
  mutate(iso3c = "ARE") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_tun_final <- farms_tun %>%
  mutate(iso3c = "TUN") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

```{r}
all_points_twn <- rbind(milkfish_points, grouper_points) %>%
  dplyr::mutate(iso3c = "TWN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_cri <- data.frame(lat = c(9.423478373794573),
                        lon = c(-84.20910189917947)) %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_egy <- data.frame(lat = c(31.360400495764903, 31.15023941171644, 31.319036258284083, 31.491306679824632, 31.52619128473819, 31.275726202441984, 29.944394112057978, 27.80632012228518),
                        lon = c(27.236078999801336, 29.81109569981684, 30.225935332660324, 31.4278324391214, 31.849352783373792, 32.30190584291966, 32.54627145839493,  34.29387671355847),
                        rgn_production = c(5, 1521, 20376, 5460, 55551, 16233, 750, 30),
                        subrgn_name = c("Mersa Matruh", "Alexandria", "Behira", "Dakahlia", "Damietta", "Port Said", "Suez", "South Sinai")) %>%
  mutate(iso3c = "EGY") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

```{r}
farms_ind <- data.frame(lat = c(9.28696221512509),
                        lon = c(79.13007737814245)) %>%
  mutate(iso3c = "IND") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_sgp_final <- farms_sgp %>%
  mutate(iso3c = "SGP") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

Now lets map the farms 
```{r}
farms_mys <- data.frame(lat=c(2.131733588116292, 2.8071936098459522, 5.384539285193906, 2.8056383383493353, 2.1305137929032876),
                        lon=c(102.40118069215845, 103.49758024234029, 100.35040003558889, 103.49881667894354, 102.40627304737939)) %>%
  mutate(iso3c = "MYS") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

```{r}
farms_bgd <- data.frame(lat=c(21.802433819366538),
                        lon=c(90.40418040967)) %>%
  mutate(iso3c = "BGD") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

```{r}
farms_khm <- data.frame(lat=c(10.53427341558665, 10.748668380457524, 10.647924480438327),
                        lon=c(103.57357940185497, 103.6089106992865, 103.5006922685572)) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_kor_final <- farms_kor %>%
  mutate(iso3c = "KOR") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

farms_phl_final <- farms_phl %>%
  mutate(iso3c = "PHL") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially")

@@

```{r}
farms_hkg <- data.frame(lat_lon = c("22.537974350807968, 114.22465750899093", "22.549021238266082, 114.27266261841545", "22.549243173819686, 114.29054140885648", "22.545901930448537, 114.29912254835972", "22.524524976629923, 114.28385013462695", "22.507936457313377, 114.30641749235996", "22.47796934657302, 114.35412559932351", "22.459641511472412, 114.360272945696", "22.4435502213444, 114.35400029960742", "22.46853714662761, 114.2720207303674", "22.42337637093222, 114.27819733339493", "22.349528341786087, 114.35178911904846", "22.367924650829952, 114.31997002657292", "22.368469602475702, 114.3230438982345", "22.3691151827537, 114.30143307907038", "22.341819373881275, 114.31744391160476", "22.35464650188533, 114.26990023341041", "22.274992746117093, 114.29389242171153", "22.164051938726015, 114.25252757025574", "22.20591578796148, 114.12923505969019", "22.221779736133797, 114.12958553008323", "22.352165476146805, 114.05569941361628", "22.45358281100093, 114.2079128367368", "22.235400816169882, 114.00599898096631", "22.454708931476908, 114.22148845386273", "22.25579039550771, 114.28554310187128")) %>%
  separate(lat_lon, into = c("lat", "lon"), sep = ",") %>%
  mutate(iso3c = "HKG") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)

write.csv(all_farms_1, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon.csv"), row.names = FALSE)

write.csv(all_farms, here::here("marine/marine_fish_general/finfish_farms/data/global_finfish_farm_lat_lon_data_quality.csv"), row.names = FALSE)

### 2021-02-12 marine/salmon/salmon_farm/STEP2_salmon_farm_locations.Rmd
finished marine bivalve data quality
finished updating data quality flags. Still need to buffer points into water for some

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL")

@@

farms_nor <- sub_norway %>% 
  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") # Counting duplicate liscense locations once

@@

farms_scotland$subregion <- sub_scotland$subregion
farms_scotland <- farms_scotland %>%
  mutate(iso3c="GBR")

@@

farms_fro <- data.frame(do.call(rbind, st_geometry(fro_pts_latlon))) 
names(farms_fro) <- c("lon", "lat")
farms_all_fro <- farms_fro %>%
  cbind(iso3c = fro_pts_latlon$iso3c)

@@

farms_tas <- tas_csv %>% 
  filter(species_farmed1 == "salmon" | species_farmed2 == "salmon" | species_farmed3 == "salmon") %>%
  dplyr::select(lon, lat) %>%
  mutate(iso3c="AUS")

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon))) 
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN")

@@

farms_nb <- data.frame(do.call(rbind, st_geometry(nb_pts_latlon))) 
names(farms_nb) <- c("lon", "lat")
farms_nb <- farms_nb %>%
  mutate(iso3c="CAN")

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN")

@@

farms_new_lab <- new_lab %>%
  mutate(iso3c = "CAN") %>%
  dplyr::select(lon, lat, iso3c)

@@

farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
  mutate(iso3c = "USA") %>%
  dplyr::select(lon, lat, iso3c)

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
names(farms_us_ne) <- c("lon", "lat")
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA")

@@

farms_nzl <- data.frame(do.call(rbind, st_geometry(nzl_pts_latlon))) 
names(farms_nzl) <- c("lon", "lat")
farms_all_nzl <- farms_nzl %>%
  cbind(iso3c = nzl_pts_latlon$iso3c)

@@

farms_ire <- data.frame(do.call(rbind, st_geometry(ire_pts_latlon))) 
names(farms_ire) <- c("lon", "lat")
farms_ire <- farms_ire %>%
  mutate(iso3c="IRL")

@@

# lat long estimates from google earth
farms_russia <- data.frame(lon=c(33.7149),
                    lat=c(69.4953)) %>%
  mutate(iso3c = "RUS")

@@

@@

farms_JPN <- data.frame(do.call(rbind, st_geometry(JPN_pts_latlon))) 
names(farms_JPN) <- c("lon", "lat")
farms_all_JPN <- farms_JPN %>%
  cbind(iso3c = JPN_pts_latlon$iso3c)

@@

Source: 
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

farms_dk <- cbind(farms_dk, dk_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

@@

farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
  mutate(iso3c = "TUR")

@@

farms_fi <- cbind(farms_fi, fi_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME)

@@

# Sweden 
Source:
HELCOM Map and Data Service, n.d. . The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

farms_sw <- cbind(farms_sw, sw_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  filter(!is.na(lat))

@@

farms_ISL <- data.frame(do.call(rbind, st_geometry(ISL_pts_latlon))) 
names(farms_ISL) <- c("lon", "lat")
farms_all_ISL <- farms_ISL %>%
  cbind(iso3c = ISL_pts_latlon$iso3c)

@@

write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)

# all_farms <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), col_types = "ddcc")

>>>>

```
Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

# save as a dataframe
farms_chile <- data.frame(do.call(rbind, st_geometry(chile_pts))) 
names(farms_chile) <- c("lon", "lat")
farms_chile <- farms_chile %>%
  mutate(iso3c="CHL") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_nor <- sub_norway %>% 
  distinct(lon=Ø_GEOWGS84, lat=N_GEOWGS84, iso3c="NOR") %>% # Counting duplicate liscense locations once
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_scotland$subregion <- sub_scotland$subregion
farms_scotland <- farms_scotland %>%
  mutate(iso3c = "GBR") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_fro <- data.frame(do.call(rbind, st_geometry(fro_pts_latlon))) 
names(farms_fro) <- c("lon", "lat")
farms_all_fro <- farms_fro %>%
  cbind(iso3c = fro_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_tas <- tas_csv %>% 
  filter(species_farmed1 == "salmon" | species_farmed2 == "salmon" | species_farmed3 == "salmon") %>%
  dplyr::select(lon, lat) %>%
  mutate(iso3c="AUS") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_bc <- data.frame(do.call(rbind, st_geometry(bc_pts_latlon))) 
names(farms_bc) <- c("lon", "lat")
farms_bc <- farms_bc %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_nb <- data.frame(do.call(rbind, st_geometry(nb_pts_latlon))) 
names(farms_nb) <- c("lon", "lat")
farms_nb <- farms_nb %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ns <- data.frame(do.call(rbind, st_geometry(ns_pts_latlon))) 
names(farms_ns) <- c("lon", "lat")
farms_ns <- farms_ns %>%
  mutate(iso3c="CAN") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_new_lab <- new_lab %>%
  mutate(iso3c = "CAN") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ps <- read.csv(file.path(path, "USA/PugetSound/USA_PugetSound_AtSalmon.csv")) %>%
  mutate(iso3c = "USA") %>%
  dplyr::select(lon, lat, iso3c) %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

@@

farms_us_ne <- data.frame(do.call(rbind, st_geometry(us_ne_salmon_pts_latlon))) 
names(farms_us_ne) <- c("lon", "lat")
farms_us_ne <- farms_us_ne %>%
  mutate(iso3c = "USA") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_nzl <- data.frame(do.call(rbind, st_geometry(nzl_pts_latlon))) 
names(farms_nzl) <- c("lon", "lat")
farms_all_nzl <- farms_nzl %>%
  cbind(iso3c = nzl_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ire <- data.frame(do.call(rbind, st_geometry(ire_pts_latlon))) 
names(farms_ire) <- c("lon", "lat")
farms_ire <- farms_ire %>%
  mutate(iso3c="IRL") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

# lat long estimates from google earth
farms_russia <- data.frame(lon=c(33.7149),
                    lat=c(69.4953)) %>%
  mutate(iso3c = "RUS") %>%
  mutate(data_quality = 1) %>%
  mutate(action_needed = "country based suitability")

@@

Source: 
Aquaculture Stewardship Council Data Mapping Study, n.d. Aquaculture Stewardship Council. [Accessed November 11, 2020] 
https://gis.asc-aqua.org/arcgis_app/

@@

farms_JPN <- data.frame(do.call(rbind, st_geometry(JPN_pts_latlon))) 
names(farms_JPN) <- c("lon", "lat")
farms_all_JPN <- farms_JPN %>%
  cbind(iso3c = JPN_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

Source: 
HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

farms_dk <- cbind(farms_dk, dk_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_turkey <- data.frame(lon=c(35.193, 35.168, 37.776,  37.776, 37.788, 37.789, 37.789, 37.789, 39.812, 39.803, 40.562, 40.558),
                    lat=c(42.012, 42.015, 41.073, 41.071, 41.103, 41.106, 41.111, 41.114, 40.991, 40.994, 41.038, 41.036)) %>%
  mutate(iso3c = "TUR") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

@@

farms_fi <- cbind(farms_fi, fi_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

# Sweden 
Source:
HELCOM Map and Data Service, n.d. The Baltic Marine Environment Protection Commission. [Accessed October 12, 2020]

@@

farms_sw <- cbind(farms_sw, sw_subregions ) %>%
  dplyr::select(lon, lat, iso3c, subregion = NAME) %>%
  filter(!is.na(lat)) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

farms_ISL <- data.frame(do.call(rbind, st_geometry(ISL_pts_latlon))) 
names(farms_ISL) <- c("lon", "lat")
farms_all_ISL <- farms_ISL %>%
  cbind(iso3c = ISL_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

@@

all_farms_1 <- all_farms %>%
  dplyr::select(-data_quality, -action_needed)

write.csv(all_farms_1, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon.csv"), row.names = FALSE)

write.csv(all_farms, here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), row.names = FALSE)

# all_farms <- read_csv(here("marine/salmon/salmon_farm/data/global_salmon_farm_lat_lon_quality.csv"), col_types = "ddccd")
